Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-06-01 main.tex
Authors TODO
Add TODOs for the diagrams to draw.
Small set of updates

This archetype can be used to train memory-$n$ strategies with the parameters
$n_1=0$ and $m_1=m_2=n$. For $n=1$, the result is WSLS.
% TODO: doublecheck that it is WSLS

@@

@@

The strategies that win the most matches are Defector, Aggrevater, and then a
series of ensemble strategies called MetaWinner, that combine the strategies
of many other strategies and take a consensus vote for each move. These are
followed by handshaking and zero determinant strategies.

@@

All training code is available on github. The are objective functions for
* total payoff
* total payoff difference
* total Moran process wins (fixation probability)

@@

>>>>

This archetype can be used to train deterministic memory-$n$ strategies with the
parameters $n_1=0$ and $m_1=m_2=n$. For $n=1$, the resulting strategy cooperates
if the last round was mutual cooperation and defects otherwise.

Two strategies in the library, Winner12 and Winner21, from \cite{Mathieu2015},
are based on lookup tables for $n_1 = 0$, $m_1 = 1$, and $m_2=2$. The strategy
Winner12 emerged in less than 10 generations of training in our framework using
a score maximizing objective.

@@

Because these strategies inherit many of the properties of the strategies
on which they are based, including using the match length to defect on the last
rounds of play, these strategies were omitted from the tournament results.

@@

The strategies that win the most matches are Defector, Aggravater, followed by
handshaking and zero determinant strategies.

@@

All training code is available on github. There are objective functions for
* total payoff
* total payoff difference
* total Moran process wins (fixation probability)

@@

% TODO: author contributions
